### 2014-02-27 paper/formal.tex
more

>>>>

Intuitively, we can now state that a language satisfies non-interference if an
attacker at level |l| cannot distinguish the runs of any two |l|-equivalent
configurations.
%
This precise NI property is called termination sensitive non-interference
(TSNI), since it considers runs of programs, and thus does not allow for leaks
due termination or internal timing behavior.
%
Formally, we define TSNI as follows.
